Title Goes Here

### 2020-05-05 analysis/paper/paper.Rmd
try to figure out the artifact number per site

>>>>

## Reference: site and number of artifacts
 cv_by_site_df_label_1 <- 
df_sitename %>% 
  select(-SPstage.Stage) %>% 
  group_by(sitename) %>% 
  add_tally() %>% 
   mutate(label = as.factor(paste0(sitename,'\nN = ',n))) %>%   select(-n) %>% 
 nest(-sitename, -label) %>% 
  mutate(cv_by_site = map(data, ~map_df(.x, cv)))

cv_by_site_df_unnest_label_1 <-   
cv_by_site_df_label_1 %>% 
  unnest(cv_by_site)
